\textbf{ Joystream: A Protocol for User Governed Content Platforms }

### 2019-02-25 paper.tex
Fix singular/plural mix

When an identifier fields are used in definitions, assume that they are unique, and that the are created by auto-incrementation in the context of some set of existing instances.

>>>>

When identifier fields are used in definitions, assume that they are unique, and that the are created by auto-incrementation in the context of some set of existing instances.
